Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Center all the images properly and add some text inside the correlations section

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Application flow of the Go tool.}
  \end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Application flow of the Go tool.}
  \end{figure}

>>>>

In this section we present our results to the research questions we set to answer. We have computed charts for all 
independent variables using either scatter plots for continuous variables (e.g. number of comments/time-to-close) 
or bar charts for categorical variables (e.g. presence of attachments). We also computed statistical analysis for 
all variables to test their significance and rank correlation coefficient and we will present each of them in their 
corresponding subsection. Lastly, we also discuss possible reasons why certain correlations occured.

@@

\begin{figure}[ht]
  \begin{center}
  \includegraphics[scale=0.23]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Attachments analysis.}
\end{figure}

Attachments are, as mentioned previously, files attached to software tickets that can take any form - from code 
snippets written in Java to tar archives. We have analyzed all the high priority tickets

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Steps to reproduce analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Stack traces analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Comments complexity analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Fields complexity analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Grammar correctness score analysis.}
\end{figure}

@@

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[scale=0.23]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Sentiment score analysis.}
\end{figure}

@@
